A Geometry for Network Visualization in \MakeLowercase{\texttt{ggplot2}}

### 2015-03-17 CC/writeup.Rnw
add les mis example code

\maketitle
\begin{abstract}
Abstract will be here
\end{abstract}

% <<readingdata, message=FALSE>>=
%  library(ggplot2)
%  theme_net <- theme(aspect.ratio = 1, line = element_blank(), panel.background = element_blank(), plot.background = element_blank(), axis.text=element_blank(),axis.title=element_blank())
%  data(blood, football, theme_elements)
%  email.net <- read.csv("~/Dropbox/ggplot2/email-data.csv") 
%  email.net <- subset(email.net, day %in% c(9,13))
%  email.names <- data.frame(name = as.factor(unique(c(as.character(email.net$From),as.character(email.net$to))))) 
% @

@@

  \subsection{Layout Argument}
  \sct{There are many layouts to choose from, but the default layout is the Kamada-Kawai layout.  This is a force-directed layout for undirected networks \citep{kamadakawai}}.
  %and the default layout changes according the size of the graph.  For smaller networks, with less than $x$ vertices and $y$ edges, the default layout is INSERT DEFAULT HERE. For larger networks with more than $x$ vertices and $y$ edges, the default layout is INSERT DEFAULT HERE. %**Now justify these two statements with research to be done.** \hh{I don't think that you'd have to defend your choices of defaults. They are defaults, and can be changed. }}
  The \texttt{layout} \sct{argument in the \texttt{geom\_net} function} can be changed to any of the layouts also found in the \texttt{sna} package, such as circular, eigen, or Fruchterman-Reingold.  \sctq{Should I insert a table of layouts here? Or maybe not since it can't actually change the layout yet? And I took out the thing about the background color because I figure it can just be changed with \texttt{theme()}} %Finally, the background color of the graph can be changed with the \texttt{bgfill} aesthetic.  This aesthetic takes only the identity colors, not additional variables.%\footnote{Sam's notes: I'm not sure if what I've laid out here is possible or even reasonable.  I have not yet found any research into what layout is best based on number of edges, number of vertices, density of the network, or anything else. \hh{You're fine - those are things, which people are going to have strong opinions on without actual backup. You provide the environment for people to easily use network data in a familiar setting.}}

\section{Many Many Examples}
\sctq{Format-wise, is it ok if each example is its own subsection?}\\
\sct{
In this section, we demonstrate the capabilities of \texttt{geom\_net} in a series of examples. 
  \subsection{Blood Donation}
  \sctq{I had to comment out all the code chunks for now. Not sure why but it won't compile if they're there.}
  \emph{Note: would be best with labels and direction}
% # <<blood_ex>>=
% # ggplot(data = blood$edges, aes(from_id = from, to_id = to)) + geom_net(vertices = blood$vertices) + expand_limits(x = c(-5,5), y = c(-5,5)) + theme_net #add vlabel later
% # @
  \subsection{Email Network}
  \emph{Note: would be best with labels and direction}
% # <<email_ex>>=
% # ggplot(data = email.net, aes(from_id = From, to_id = to, ealpha = 0.1,vsize = 2)) + geom_net(vertices = email.names) + expand_limits(x=c(-1,5), y = c(-1,5)) + facet_wrap(~day) + theme_net
% # @
  \subsection{\texttt{ggplot2} Theme Elements}
  \emph{Note: would be best with labels and direction}
% # <<theme_ex>>=
% # #ggplot(data = theme_elements$edges, aes(from_id = child, to_id = parent)) + geom_net(vertices = theme_elements$vertices) + expand_limits(x = c(-5,5), y = c(-5,5)) + theme_net
% # @
  \subsection{Madmen Network (again?? or no?)}
  \sctq{leaving blank for now.}
  \subsection{College Football}
  \emph{Note: would be best with coloring vertices by conference} \citet{football}
% # <<football_ex>>=
% # ggplot(data = football$edges, aes(from_id = from, to_id = to)) + geom_net(vertices = football$vertices) + expand_limits(x = c(-2.5,2.5), y = c(-2.5,2.5)) + theme_net
% # @
  \subsection{Les Mis\'{e}rables}
  \emph{Haven't looked at this one yet. Just found it on MEJ Newmans website.  http://www-personal.umich.edu/~mejn/netdata/}
}

>>>>

\maketitle
\begin{abstract}
Abstract will be here
\end{abstract}
<<chunk_setup, echo=FALSE>>=
opts_chunk$set(echo=FALSE, message = FALSE)
@
<<readingdata, message=FALSE, echo=FALSE>>=
 library(knitr)
 library(ggplot2)
 theme_net <- theme(aspect.ratio = 1, line = element_blank(), panel.background = element_blank(), plot.background = element_blank(), axis.text=element_blank(),axis.title=element_blank())
 data(blood, football, theme_elements)
 email.net <- read.csv("~/Dropbox/ggplot2/email-data.csv") 
 email.net <- subset(email.net, day %in% c(9,13))
 email.names <- data.frame(name = as.factor(unique(c(as.character(email.net$From),as.character(email.net$to))))) 
@

@@

  \subsection{Layout Argument}
  \sct{There are many layouts to choose from, but the default layout is the Kamada-Kawai layout.  This is a force-directed layout for undirected networks \citep{kamadakawai}}.
  %and the default layout changes according the size of the graph.  For smaller networks, with less than $x$ vertices and $y$ edges, the default layout is INSERT DEFAULT HERE. For larger networks with more than $x$ vertices and $y$ edges, the default layout is INSERT DEFAULT HERE. %**Now justify these two statements with research to be done.** \hh{I don't think that you'd have to defend your choices of defaults. They are defaults, and can be changed. }}
  The \texttt{layout} \sct{argument in the \texttt{geom\_net} function} can be changed to any of the layouts also found in the \texttt{sna} package, such as circular, eigen, or Fruchterman-Reingold.  \sctq{Should I insert a table of layouts here? And I took out the thing about the background color because I figure it can just be changed with \texttt{theme()}} %Finally, the background color of the graph can be changed with the \texttt{bgfill} aesthetic.  This aesthetic takes only the identity colors, not additional variables.%\footnote{Sam's notes: I'm not sure if what I've laid out here is possible or even reasonable.  I have not yet found any research into what layout is best based on number of edges, number of vertices, density of the network, or anything else. \hh{You're fine - those are things, which people are going to have strong opinions on without actual backup. You provide the environment for people to easily use network data in a familiar setting.}}

\section{Many Many Examples}
\sctq{Format-wise, is it ok if each example is its own subsection?}\\
\sct{
In this section, we demonstrate the capabilities of \texttt{geom\_net} in a series of examples. 
  \subsection{Blood Donation}
  \sctq{I had to comment out all the code chunks for now. Not sure why but it won't compile if they're there.}
  \emph{Note: would be best with labels and direction}\\
  In this network, there are eight nodes and 27 edges.  The nodes represent the eight different blood types possible in humans
%<<blood_ex,highlight=TRUE>>=
%ggplot(data = blood$edges, aes(from_id = from, to_id = to)) + geom_net(vertices = blood$vertices) + expand_limits(x = c(-5,5), y = c(-5,5)) + theme_net #add vlabel later
%@
  \subsection{Email Network}
  \emph{Note: would be best with labels and direction}
% # <<email_ex>>=
% # ggplot(data = email.net, aes(from_id = From, to_id = to, ealpha = 0.1,vsize = 2)) + geom_net(vertices = email.names) + expand_limits(x=c(-1,5), y = c(-1,5)) + facet_wrap(~day) + theme_net
% # @
  \subsection{\texttt{ggplot2} Theme Elements}
  \emph{Note: would be best with labels and direction}
% # <<theme_ex>>=
% # #ggplot(data = g$edges, aes(from_id = child, to_id = parent)) + geom_net(vertices = g$vertices) + expand_limits(x = c(-5,5), y = c(-5,5)) + theme_net
% # @
  \subsection{Madmen Network (again?? or no?)}
  \sctq{leaving blank for now.}
  \subsection{College Football}
  \emph{Note: would be best with coloring vertices by conference} \citet{football}
% # <<football_ex>>=
% # ggplot(data = football$edges, aes(from_id = from, to_id = to)) + geom_net(vertices = football$vertices) + expand_limits(x = c(-2.5,2.5), y = c(-2.5,2.5)) + theme_net
% # @
  \subsection{Les Mis\'{e}rables}
  \emph{Note: data set has edge weightings for number of co-occurences of characters. esize would be useful here!}
% <<lesmis_ex>>=
% ggplot(data = lesmis$edges, aes(from_id = from, to_id = to)) + geom_net(vertices = lesmis$vertices, aes(esize = value), layout = 'fruchtermanreingold') + expand_limits(x = c(-25,25), y = c(-25,25)) + theme_net
% @
}
